\bf Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-07-10 manuscript/main.tex
intro draft

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[comma,authoryear]{natbib} 
\usepackage[margin=1in]{geometry}

\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{verbatim}

\newtheorem{proposition}{Proposition}
\newtheorem{alg}{Algorithm} 
\newtheorem{theorem}{Theorem}
\newtheorem{assumption}{Assumption}
\newtheorem{note}[theorem]{Note}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{define}[theorem]{Definition}
% \newtheorem{denote}[theorem]{denote}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}{Lemma}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage[flushleft]{threeparttable}
\usepackage[labelfont=bf]{caption}
\usepackage{caption,booktabs,array}
\usepackage{multirow}
\usepackage{makecell}
\usepackage[usenames, dvipsnames]{color}
\usepackage{setspace}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{rotating}
\usepackage{url}
\usepackage{enumerate}
\allowdisplaybreaks
\usepackage{bbold}
\usepackage{xcolor}         % colors
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{hyperref}

\setstretch{1.8} % For 25 lines per page

\DeclareMathOperator*{\argmax}{arg\,max}

@@

\title{Partial Least Squares Regression with Multiple Functional and Scalar Predictors}
\author{Jongmin Mun and Jeong Hoon Jang}
\date{\today}

\begin{document}
	\maketitle

	\section{Introduction} \label{sec: Introduction}
	Functional regression settings involving a large number of predictors, $X_{i1}(t), X_{i2}(t), \ldots, X_{iK}(t)$, are becoming increasingly common. For example, \cite{storeySignificanceAnalysisTime2005} analyzes two gene expression datasets measured over time, which involve only a small number of patients but tens of thousands of functional predictors.

	Infinite dimensional beta estimation problem (ill-posed problem)

	Multicollinearity and high-dimensionality in scalar predictors are not handled.

	Also, there may be high correlation between functional and scalar predictors.

	Many approaches have been proposed
	1. Roughness Penalty
	2. basis approach (power-series, B-splines, wavelets)
	- Power Series splines (Goldsmith et al., 2011, Journal of Computational Statistics)
	- B-splines (H. Cardot, F. Ferraty, P. Sarda, Spline estimators for the functional linear model, Statistica Sinica 13 (2003) 571–591.
	T.T.Cai,P.Hall,Prediction in functional linear regression, Ann.Stat. 34(5) (2006) 2159–2179.)
	- Wavelet (Y.Zhao,R.T.Ogden,P.T.Reiss,Wavelet-based lasso in functional linear regression, J.Comput.Graph.Stat.21(3)(2012)600–61.)7

	3. FPCA approach
	- Hall, P. and Horowitz, J. L. (2007), ‘Methodology and convergence rates for functional linear regression’, The Annals of Statistics 35(1), 70–91.
	- Reiss P. T.,  Ogden R. T.. Functional principal component regression and functional partial least squares, Journal of the American Statistical Association, 2007, vol. 102 (pg. 984-996)
	- Febrero-Bande et al., 2017

	4. FPLS Approach
	- Preda and Saporta (2005)
	- Reiss and Odgen, 2007
	- Aguilera AM, Escabias M, Preda C, Saporta G. Using basis expansions for estimating functional PLS regression applications withchemometric data.Chemom Intell Lab Syst. 2010;104:289-305.
	- Delaigle and Hall, 2012
	- Febrero-Bande et al., 2017
	- Beyaztas and Shang, (2022) A Robust Functional Partial Least Squares for Scalar-on-Multiple-Function Regression. Journal of Chemometrics.
	- Saricam et al., On partial least-squares estimation in scalar-on-function regression models. Journal of Chemometrics.
	- Mutis  et al. (2025) On function-on-function linear quantile regression

@@

	\begin{enumerate}
		\item Independent variables consist of multiple highly structured images and scalar predictors.
		\item Our sample size is small compared to the dimension and number of functional and scalar predictors.
		\item Existing partial least squares (PLS) methods can only accommodate (i) univariate or multivariate functional predictors without any scalar predictors \citep{Preda2005, Delaigle2012, Febrero2017, Beyaztas2020}; or (2) a univariate functional predictor with other scalar predictors \citep{Wang2018}.
	\end{enumerate}

@@

				&\argmax \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top}(J^\ast+\Lambda \ddot{J}^\ast) \xi^*} , \quad \textit{or equivalently}, \\ 
				&\argmax \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1.

@@

	\begin{algorithm}[b!]
		\caption{Hybrid PLS (under construction)}
		\label{alg:main}
		\begin{algorithmic}[1]
			\Require 
			Response $\mathbf{y} \in \mathbb{R}^n$,
			%functional predictor evalulation points $\mathbf{t}_1, \ldots, \mathbf{t}_m \in [0,1]^K,$
			hybrid predictors approximation coefficient
			$\widetilde{C}^* \ \in \mathbb{R}^{n \times (MK+p)} $ \eqref{eq: basis approximation of W},
			Gram matrix with respect to basis functions
			$J^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)} $
			\eqref{def:J_and_J_star},
			Gram matrix with respect to second derivatives of the basis functions 
			$\ddot{J}^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)}$
			\eqref{def:J_dotdot_ast},
			regularization matrix $\Lambda  \in \mathbb{R}^{(MK+p) \times (MK+p)}$ \eqref{def:Lambda}
			%%%%%%%%%%%%%%%%%%%%%
			\State
			$\widetilde{C}^{*[1]} \leftarrow \widetilde{C}^*$
			\For{ l = 1, 2, \ldots  $T$}
			\State $\mathbf{V}^\ast \leftarrow n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast$
			\Comment{ \eqref{def:V_star}}
			\State 	$\widehat{\xi}_l^\ast \leftarrow \argmax_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1
			$
			\Comment{ \eqref{eq: Regularized generalized rayleigh quotient equation}} 
			\State $\widehat{\boldsymbol{\rho}}_l
			\leftarrow 
			\widetilde{C}^* J^\ast  \widehat{\xi}_l^\ast
			$
			\Comment{$\in \mathbb{R}^n$; \eqref{compute_pls_score}}
			\EndFor
			\State Output a
		\end{algorithmic}
	\end{algorithm}

@@

		\caption{Comparison of Correlation Matrices and Graph Structures under Strong and Weak Dependencies.}
		\label{fig:correlation_graph_comparison}
	\end{figure}
	\begin{comment}
		The goal of this simulation is to:
		\begin{enumerate}
			\item Utilize a graphical model to introduce a complex dependence structure.
			\item Demonstrate that our method outperforms the penalized functional regression approach by \citet{goldsmith_penalized_2011}.
			\item Show that our method exhibits superior performance as correlation strength increases.
		\end{enumerate}

@@

	The baseline methods are:
	\begin{itemize}
		\item Penalized functional regression (pfr)~\cite
		{goldsmith_penalized_2011}\item Principal component regression (fpcr): run both of PCA for multple functional predictors~\cite{happ_multivariate_2018} and scalar PCA and run OLS on the PC scores.
	\end{itemize}
	% TODO: \usepackage{graphicx} required

@@

	\subsection{Proof of new Proposition}
	For any $\xi = (\xi_1, \ldots, \xi_K, \boldsymbol{\zeta})\in \mathcal{H}$, we have:
	\begin{align*}
		\widehat{\textnormal{Cov}} (
		\langle \widetilde{W}, \xi  \rangle_{\mathcal{H}}, Y 
		) 
		&=  %1
		\frac{1}{n} 
		\sum 
		\limits_{i=1}^n 
		y_i
		\langle \widetilde{W}_i, \xi \rangle_\mathcal{H} \\
		&= %2
		\frac{1}{n} 
		\sum \limits_{i=1}^n
		y_i
		\biggl(
		\sum_{j=1}^K
		\langle \widetilde{X}_{ij}, \xi_j \rangle  
		+
	 \mathbf{Z}_i^\top 
		\boldsymbol{\zeta} 
		\biggr)
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\\&= %3
		\frac{1}{n}
		\sum
		\limits_{i=1}^n 
		y_i
		\biggl( \sum \limits_{k=1}^K \int_0^1 \widetilde{X}_{ij}(t) \, \xi_j(t) \, dt \biggr)
		+
		 \frac{1}{n}
		 \sum
		 \limits_{i=1}^n
		 y_i
		 ( \mathbf{Z}_i^\top \boldsymbol{\zeta} )
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		  \\&=  
		  \frac{1}{n} \sum \limits_{i=1}^n 
		  y_i
		\biggl\{ 
		  \sum \limits_{k=1}^K \int_0^1
		   \biggl(
		   \sum_{m=1}^M \theta_{ijm} b_{m}(t) 
		   \biggr) 
		   \biggl(
		   \sum_{m'=1}^M d_{jm'} b_{m'}(t) 
		   \biggr) 
		   dt
		\biggr\}  
		  +
	\frac{1}{n}
	\mathbf{y}^\top
	Z \boldsymbol{\zeta} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\\&=  
\frac{1}{n} \sum \limits_{i=1}^n 
y_i
\biggl\{ 
\sum \limits_{k=1}^K 
\sum_{m=1}^M
\sum_{m'=1}^M  
\theta_{ijm}
d_{jm'}
\int_0^1
 b_{m}(t) 
 b_{m'}(t) 
dt
\biggr\}  
+
\frac{1}{n}
\mathbf{y}^\top
Z \boldsymbol{\zeta} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\\&=  
\sum \limits_{k=1}^K 
\biggl\{
\frac{1}{n} \sum \limits_{i=1}^n 
y_i
(
\boldsymbol{\theta}_{ij}^\top
B
\mathbf{d}_j
)  
\biggr\}
+
\frac{1}{n}
\mathbf{y}^\top
Z \boldsymbol{\zeta}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\\&=  
\frac{1}{n}
\biggl(
\sum \limits_{k=1}^K 
\mathbf{y}^\top
\Theta_{j}
B
\mathbf{d}_j
+
\mathbf{y}^\top
Z \boldsymbol{\zeta} 
\biggr).
	\end{align*}

The squared hybrid Hilbert norm $\langle {\xi},{\xi} \rangle_{\mathcal{H}}$ 
is computed as follows:
\begin{align*}
\langle {\xi},{\xi} \rangle_{\mathcal{H}}
&=
\sum_{j=1}^K
\langle
\xi_j, \xi_j
\rangle
+
\boldsymbol{\zeta}^\top \boldsymbol{\zeta}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\\&=
\sum \limits_{k=1}^K \int_0^1
\biggl(
\sum_{m=1}^M d_{jm'} b_{m}(t) 
\biggr) 
\biggl(
\sum_{m'=1}^M d_{jm'} b_{m'}(t) 
\biggr) 
dt
+
\boldsymbol{\zeta}^\top \boldsymbol{\zeta}  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\\&=
aaaaa
\end{align*}
admits the following matrix representation:
	\[
	\langle \boldsymbol{\xi}, \boldsymbol{\xi} \rangle_{\mathcal{H}} = \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{d}_j + \boldsymbol{\zeta}^\top \boldsymbol{\zeta}.
	\]

@@

	and  $\xi^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$. Then, the $l$-th PLS component, $\widehat{\xi} \equiv \widehat{\xi}_l$ can be obtained by solving
	\begin{equation}\label{def:eigenproblem_smoothed}
		\argmax \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top} J^\ast \xi^*}, \quad \textit{or equivalently}, \quad \argmax \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} J^\ast \xi^*=1,
	\end{equation}
	with respect to $\widehat{\xi}^*=(\widehat{\mathbf{a}}^{\top}, \widehat{\boldsymbol{\theta}}^{\top})^\top$

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL 
\usepackage{bibunits}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{verbatim}

%%%%

\usepackage{graphicx}
\usepackage{multirow}
\usepackage{hhline}
%\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{bm}
\usepackage{multirow,multicol}
\usepackage{verbatim}
\usepackage{amsfonts,amssymb,amsthm,color,authblk}
\usepackage{xcolor}
\definecolor{myblue}{RGB}{0, 0, 0}
\newcommand{\blue}[1]{{\color{myblue}#1}}
%%%%

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{1}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{condition}{Condition}
\newtheorem{remark}{Remark}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-1in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.7in}%
\addtolength{\topmargin}{-1in}%

%\usepackage{etoolbox}
%\AtBeginBibliography{\small\setlength{\baselineskip}{10pt}}
%\setlength{\bibsep}{0pt plus 0.2ex} 
\usepackage{setspace}   
\usepackage{etoolbox}  
\usepackage{algorithm}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

\usepackage[noend]{algpseudocode}
\usepackage{hyperref}

\AtBeginEnvironment{thebibliography}{\small\setstretch{0.93}}

\begin{document}

%\bibliographystyle{natbib}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if1\blind
{
  \title{\bf Partial Least Squares Regression with Multiple Functional and Scalar Predictors
  }
  \author{Jongmin Mun  $^1$  and Jeong Hoon Jang$^2$
\medskip\\
University of Southern California$^1$ and University of Texas Medical Branch$^2$
\\
}
\date{\today}

  \maketitle
} \fi

\if0\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf SOFARI: High-Dimensional Manifold-Based Inference}
\end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
abstract.
\end{abstract}

\noindent%
{\it Keywords:}  dimension reduction; functional data analysis; multiple data modalities; multivariate data analysis; multivariate functional data; partial least square

\vfill

%\newpage
\spacingset{1.9} % DON'T change the spacing!

%\begin{bibunit}[agsm]

\section{Introduction} \label{sec: Introduction}
Functional data analysis (FDA) treats each observed process as a realization of a random function over a continuous domain, such as time or space. The smoothness and infinite-dimensional nature of functional data allow researchers to exploit rich structural features, including derivatives and complex covariance patterns. This enables regression analysis for predicting clinical outcomes using complex functional predictors collected with advanced recording technologies, such as medical imaging data.

In modern biomedical studies, it is increasingly common to collect heterogeneous data modalities for each subject. For instance, the Emory University renal study \citep{changBayesianLatentClass2020, jangPrincipalComponentAnalysis2021} records both multiple renogram curves (functional data) and multiple renogram variables (vector data) per kidney, capturing distinct yet related physiological information. Such settings call for statistical methods that can jointly model functional and vector-valued covariates to account for both shared and modality-specific variation linked to clinical outcomes.

%Infinite dimensional beta estimation problem (ill-posed problem)
%Multicollinearity and high-dimensionality in scalar predictors are not handled.
%Also, there may be high correlation between functional and scalar predictors.
Regression with functional and scalar predictors poses several challenges. Estimating the infinite-dimensional slope function is an ill-posed problem requiring regularization or dimension reduction. Scalar predictors are often high-dimensional and multicollinear, further complicating estimation. Moreover, strong correlations between functional and scalar predictors are common but typically overlooked by separate modeling approaches. These issues call for a unified framework that addresses ill-posedness, high-dimensionality, and cross-modality correlation jointly.

Many approaches have been proposed
1. Roughness Penalty
2. basis approach (power-series, B-splines, wavelets)
- Power Series splines \citep{goldsmithPenalizedFunctionalRegression2011}
- B-splines \citep{cardotSplineEstimatorsFunctional2003, caiPredictionFunctionalLinear2006}
- Wavelet\citep{zhaoWaveletbasedLASSOFunctional2012}

%3. FPCA approach
One possible approach is to apply principal component analysis, FPCA or MFPCA for the functional predictors and standard PCA for the scalar predictors, followed by classical multivariate regression on the resulting scores. 
This PCA regression strategy has been well-studied for functional predictors alone \citep{hallMethodologyConvergenceRates2007, reissFunctionalPrincipalComponent2007, febrero-bandeFunctionalPrincipalComponent2017}, but it overlooks potentially strong correlations between functional and scalar components, leading to multicollinearity and suboptimal predictive performance. Outside the regression context, \citet{jangPrincipalComponentAnalysis2021} proposed a joint PCA method that accounts for correlation between functional and scalar data. However, the resulting components are not informed by the response and may fail to capture directions of maximal correlation with the outcome.

%4. FPLS Approach
Partial least squares (PLS) regression offers a powerful alternative by explicitly seeking low-dimensional projections of the predictors that maximize their covariance with the outcome. While PLS has been extensively studied in the context of functional data, both for single and multiple functional predictors \citep{predaPLSRegressionStochastic2005, reissFunctionalPrincipalComponent2007, aguileraUsingBasisExpansions2010, delaigleMethodologyTheoryPartial2012, aguileraPenalizedVersionsFunctional2016, febrero-bandeFunctionalPrincipalComponent2017, beyaztasRobustFunctionalPartial2022, saricamPartialLeastsquaresEstimation2022, mutisFunctiononfunctionLinearQuantile2025}, a unified framework capable of simultaneously handling mixed modalities of functional and scalar covariates remains underdeveloped.

In this paper, we propose a hybrid partial least squares (PLS) regression framework that integrates functional and vector predictors in a principled and coherent manner. To extract predictive structure from jointly observed and potentially correlated data types, we define a Hilbert space that treats functional and vector components as a single hybrid object, equipped with a suitable inner product. The hybrid PLS direction is then obtained by iteratively maximizing the empirical covariance with the response, subject to a unit-norm constraint in this Hilbert space.

@@

\begin{enumerate}
	\item Independent variables consist of multiple highly structured images and scalar predictors.
	\item Our sample size is small compared to the dimension and number of functional and scalar predictors.
	\item Existing partial least squares (PLS) methods can only accommodate (i) univariate or multivariate functional predictors without any scalar predictors \citep{predaPLSRegressionStochastic2005, delaigleMethodologyTheoryPartial2012, Febrero2017, Beyaztas2020}; or (2) a univariate functional predictor with other scalar predictors \citep{Wang2018}.
\end{enumerate}

@@

			&\arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top}(J^\ast+\Lambda \ddot{J}^\ast) \xi^*} , \quad \textit{or equivalently}, \\ 
			&\arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1.

@@

\begin{algorithm}[b!]
	\caption{Hybrid PLS (under construction)}
	\label{alg:main}
	\begin{algorithmic}[1]
		\Require 
		Response $\mathbf{y} \in \mathbb{R}^n$,
		%functional predictor evalulation points $\mathbf{t}_1, \ldots, \mathbf{t}_m \in [0,1]^K,$
		hybrid predictors approximation coefficient
		$\widetilde{C}^* \ \in \mathbb{R}^{n \times (MK+p)} $ \eqref{eq: basis approximation of W},
		Gram matrix with respect to basis functions
		$J^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)} $
		\eqref{def:J_and_J_star},
		Gram matrix with respect to second derivatives of the basis functions 
		$\ddot{J}^\ast \in \mathbb{R}^{(MK+p) \times (MK+p)}$
		\eqref{def:J_dotdot_ast},
		regularization matrix $\Lambda  \in \mathbb{R}^{(MK+p) \times (MK+p)}$ \eqref{def:Lambda}
		%%%%%%%%%%%%%%%%%%%%%
		\State
		$\widetilde{C}^{*[1]} \leftarrow \widetilde{C}^*$
		\For{ l = 1, 2, \ldots  $T$}
		\State $\mathbf{V}^\ast \leftarrow n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast$
		\Comment{ \eqref{def:V_star}}
		\State 	$\widehat{\xi}_l^\ast \leftarrow \arg \max_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1
		$
		\Comment{ \eqref{eq: Regularized generalized rayleigh quotient equation}} 
		\State $\widehat{\boldsymbol{\rho}}_l
		\leftarrow 
		\widetilde{C}^* J^\ast  \widehat{\xi}_l^\ast
		$
		\Comment{$\in \mathbb{R}^n$; \eqref{compute_pls_score}}
		\EndFor
		\State Output a
	\end{algorithmic}
\end{algorithm}

@@

	\caption{Comparison of Correlation Matrices and Graph Structures under Strong and Weak Dependencies.}
	\label{fig:correlation_graph_comparison}
\end{figure}

\begin{comment}
	The goal of this simulation is to:
	\begin{enumerate}
		\item Utilize a graphical model to introduce a complex dependence structure.
		\item Demonstrate that our method outperforms the penalized functional regression approach by \citet{goldsmithPenalizedFunctionalRegression2011}.
		\item Show that our method exhibits superior performance as correlation strength increases.
	\end{enumerate}

@@

The baseline methods are:
\begin{itemize}
	\item Penalized functional regression (pfr)~\cite
	{goldsmithPenalizedFunctionalRegression2011}\item Principal component regression (fpcr): run both of PCA for multple functional predictors~\cite{happ_multivariate_2018} and scalar PCA and run OLS on the PC scores.
\end{itemize}
% TODO: \usepackage{graphicx} required

@@

\subsection{Proof of new Proposition}
For any $\boldsymbol{\xi} = (\xi_1, \ldots, \xi_K, \boldsymbol{\zeta}) \in \mathcal{H}$, where each functional component $\xi_j \in L^2([0,1])$ lies in the span of the basis functions $\{b_1(t), \ldots, b_M(t)\}$ and is expressed as
\begin{equation*}
	\xi_j(t) := 
	\sum_{m=1}^M d_{jm} \, b_m(t), \quad j = 1, \ldots, K,
\end{equation*}
with coefficient vectors $\mathbf{d}_j := (d_{j1}, \ldots, d_{jM})^\top \in \mathbb{R}^M$, the squared norm of $\boldsymbol{\xi}$ in the hybrid Hilbert space $\mathcal{H}$ is given by
is computed as follows:
\begin{align*}
	\langle {\xi},{\xi} \rangle_{\mathcal{H}}
	&=
	\sum_{j=1}^K
	\langle
	\xi_j, \xi_j
	\rangle
	+
	\boldsymbol{\zeta}^\top \boldsymbol{\zeta}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\\&=
	\sum \limits_{j=1}^K \int_0^1
	\biggl(
	\sum_{m=1}^M d_{jm} b_{m}(t) 
	\biggr) 
	\biggl(
	\sum_{m'=1}^M d_{jm'} b_{m'}(t) 
	\biggr) 
	dt
	+
	\boldsymbol{\zeta}^\top \boldsymbol{\zeta}  
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\\&=
	\sum \limits_{j=1}^K 
	\sum_{m=1}^M
	\sum_{m'=1}^M
	d_{jm}
	d_{jm'}
	\int_0^1
	b_{m}(t) 
	b_{m'}(t) 
	dt
	+
	\boldsymbol{\zeta}^\top \boldsymbol{\zeta}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\\&=
	\sum \limits_{j=1}^K 
	\mathbf{d}_j^\top
	\Theta_j
	\mathbf{d}_j
	+
	\boldsymbol{\zeta}^\top \boldsymbol{\zeta}
\end{align*}
\begin{align*}
	\widehat{\textnormal{Cov}} (
	\langle \widetilde{W}, \xi  \rangle_{\mathcal{H}}, Y 
	) 
	&=  %1
	\frac{1}{n} 
	\sum 
	\limits_{i=1}^n 
	y_i
	\langle \widetilde{W}_i, \xi \rangle_\mathcal{H} \\
	&= %2
	\frac{1}{n} 
	\sum \limits_{i=1}^n
	y_i
	\biggl(
	\sum_{j=1}^K
	\langle \widetilde{X}_{ij}, \xi_j \rangle  
	+
	\mathbf{Z}_i^\top 
	\boldsymbol{\zeta} 
	\biggr)
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\\&= %3
	\frac{1}{n}
	\sum
	\limits_{i=1}^n 
	y_i
	\biggl( \sum \limits_{k=1}^K \int_0^1 \widetilde{X}_{ij}(t) \, \xi_j(t) \, dt \biggr)
	+
	\frac{1}{n}
	\sum
	\limits_{i=1}^n
	y_i
	( \mathbf{Z}_i^\top \boldsymbol{\zeta} )
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\\&=  
	\frac{1}{n} \sum \limits_{i=1}^n 
	y_i
	\biggl\{ 
	\sum \limits_{k=1}^K \int_0^1
	\biggl(
	\sum_{m=1}^M \theta_{ijm} b_{m}(t) 
	\biggr) 
	\biggl(
	\sum_{m'=1}^M d_{jm'} b_{m'}(t) 
	\biggr) 
	dt
	\biggr\}  
	+
	\frac{1}{n}
	\mathbf{y}^\top
	Z \boldsymbol{\zeta} 
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\\&=  
	\frac{1}{n} \sum \limits_{i=1}^n 
	y_i
	\biggl\{ 
	\sum \limits_{k=1}^K 
	\sum_{m=1}^M
	\sum_{m'=1}^M  
	\theta_{ijm}
	d_{jm'}
	\int_0^1
	b_{m}(t) 
	b_{m'}(t) 
	dt
	\biggr\}  
	+
	\frac{1}{n}
	\mathbf{y}^\top
	Z \boldsymbol{\zeta} 
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\\&=  
	\sum \limits_{k=1}^K 
	\biggl\{
	\frac{1}{n} \sum \limits_{i=1}^n 
	y_i
	(
	\boldsymbol{\theta}_{ij}^\top
	B
	\mathbf{d}_j
	)  
	\biggr\}
	+
	\frac{1}{n}
	\mathbf{y}^\top
	Z \boldsymbol{\zeta}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\\&=  
	\frac{1}{n}
	\biggl(
	\sum \limits_{k=1}^K 
	\mathbf{y}^\top
	\Theta_{j}
	B
	\mathbf{d}_j
	+
	\mathbf{y}^\top
	Z \boldsymbol{\zeta} 
	\biggr).
\end{align*}	
Both expressions in \eqref{...} and \eqref{...} can be represented as inner products in the product space $(\mathbb{R}^M)^K \times \mathbb{R}^p$, which is defined as follows:
\begin{lemma}[Inner product of tuples]
	\label{lemma:valid_inner_product_tuple}
	Let $B \in \mathbb{R}^{M \times M}$ be a symmetric positive semi-definite matrix. 
	For any two tuples $u = (\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta})$ and $v = (\mathbf{g}_1, \ldots, \mathbf{g}_K, \boldsymbol{\omega})$ in the product space $(\mathbb{R}^M)^K \times \mathbb{R}^p$, define the bilinear form
	\[
	\langle u, v \rangle_{B} := \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{g}_j + \boldsymbol{\zeta}^\top \boldsymbol{\omega}.
	\]
	Then $\langle \cdot, \cdot \rangle_{B}$ is a valid inner product on $(\mathbb{R}^M)^K \times \mathbb{R}^p$.
\end{lemma}
The proof of Lemma \ref{lemma:valid_inner_product_tuple} is provided in Appendix \ref{section:proof:lemma:valid_inner_product_tuple}

@@

and  $\xi^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$. Then, the $l$-th PLS component, $\widehat{\xi} \equiv \widehat{\xi}_l$ can be obtained by solving
\begin{equation}\label{def:eigenproblem_smoothed}
	\arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top} J^\ast \xi^*}, \quad \textit{or equivalently}, \quad \arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} J^\ast \xi^*=1,
\end{equation}
with respect to $\widehat{\xi}^*=(\widehat{\mathbf{a}}^{\top}, \widehat{\boldsymbol{\theta}}^{\top})^\top$
